\LARGE \bf Planning with Attitude

### 2020-10-14 paper/main.tex
typo fix

        ALTRO is able to converge on a feasible trajectory for this problem without any initial guess, with the resulting attitude history represented in Fig. \ref{fig:keepout}. Without the camera constraint present, the trajectory will pass through the keep-out
        zone, making the trajectory infeasible. With the keep-out zone constraint present, ALTRO
        is able to generate a trajctory that performs the slew in an efficient manner, while
        keeping the camera sufficiently far from the sun.

>>>>

        ALTRO is able to converge on a feasible trajectory for this problem without any initial guess, with the resulting attitude history represented in Fig. \ref{fig:keepout}. Without the camera constraint present, the trajectory will pass through the keep-out
        zone, making the trajectory infeasible. With the keep-out zone constraint present, ALTRO
        is able to generate a trajectory that performs the slew in an efficient manner, while
        keeping the camera sufficiently far from the sun.
